\subsection{Project Requirements}
\noindent The main purpose of the project is to create a file synchronizer that requires a central server to host the client and synchronize files, handle multiple simultaneous user requests, and handle conflicts. The requirement for this project is to ensure that the server can handle multiple simultaneous clients and conflicts with the same copy of the file, so we must have at least 2 clients and allow different types of users to upload files to the server. First, we need to design a desktop, which can be a command line or a background utility. In addition, we need a mobile client, which is a standalone application developed in the iOS or Android environment.




\begin{comment}
\noindent As our main task is to develop a multi-host file synchroniser,In summary, the function of this synchronizer is to make it possible to edit the same files across multiple computers in a sensible way. This synchroniser can satisfy the multiple clients access and edit the data in a single central server. In this group project, our final result is to develop a server and two clients, one for desktop and another for mobile.the function of this synchronizer is to make it possible to edit the same files across multiple computers in a sensible way. This synchroniser can satisfy the multiple clients access and edit the data in a single central server. In this group project, our final result is to develop a server and two clients, one for desktop and another for mobile.
\end{comment}



\subsection{Project Design}
\noindent The desktop client team decided to develop a web application for the user to easily upload and download files from the server using the UI instead of using the command line.
The mobile client team has decided to implement in the iOS environment because members have previously developed experience with the application in this environment.