\noindent A cloud synchronization("sync")application synchronizes data hosted by a cloud storage service(e.g.,Dropbox,Google Drive,Microsoft Google Drive,etc.) For example,Dropbox announced that it has hit a new milestone of 300 million users, adding 100 million users in just six months.\citep{7417235}

\vspace{0.2cm}
\noindent Multi-user collaboration and synchronization are nowadays essential features in cloud storage services.\citep{MOSCICKI20181052}Ideally, this kind of cloud storage can provide users with a convenient environment.In file sharing scenario, 


\vspace{0.2cm}
\noindent At present, several applications and platforms that have been successfully implemented on the market have Google Drive, Dropbox, etc., but Google Drive is more comprehensive and richer than Dropbox. Specifically, Google Drive has sophisticated and powerful sharing capabilities, and enables online editing and support for documents in different formats.

\begin{comment}
Jakub T. Mo艣cicki, Luca Mascetti,
Cloud storage services for file synchronization and sharing in science, education and research,
Future Generation Computer Systems,
Volume 78, Part 3,
2018,
Pages 1052-1054,
ISSN 0167-739X,
https://doi.org/10.1016/j.future.2017.09.019.
\end{comment}

\vspace{0.2cm}
\noindent With the collaboration feature, no matter where the participants are, whether the user is using the mobile phone or the web page, he or she can write a document together with teammates, just like sitting together to discuss. Users can see other all editorial behaviors of everyone, and can be commented or discussed in real time, this is an efficient way of working, and also the main function our group project want to achieve.

\vspace{0.2cm}
\noindent Mobile devices have changed how we conceive software. There is a great range of development alternatives.At present, mobile web applications have been widely used, and there are many examples and valuable experiences in the current development background and field.\citep{7128878}


%Current work‘s status and comparison in this field(done)

% ways and functions to achieve sync logic(main part)

%relative algorithms

%ios platform advantages and applications（done）

%drawbacks and limitations of other researches, & future work
